GGVIS PROJECT
========================================================
**Team:** Junzhao Hu (junhu), Andreea Erciulescu (andreeae), Jennifer Chang (jenchang), Guillermo Basulto-Elias (basulto)

**Description:**

The idea of today's lab is the same as the one two weeks ago: you are asked to provide a shiny applicaiton that allows the user to select US cities to be included in a route across the country.

This time, the applicaiton is supposed to be based on ggvis and enhanced by interactive functionality.

(1) Construct a map of the US using ggvis. Add points of all available cities on top of the map

```{r, eval=FALSE}
# Installs Required Libraries, including ggvis
install.packages("devtools","maps","ggplot2","shiny")
library(devtools)
devtools::install_github(c("hadley/testthat", "rstudio/shiny", "rstudio/ggvis"))

# Load Libraries
library(ggvis)
library(maps)
library(ggplot2)
library(shiny)

# Load Map of States, and US Cities data
all_states<-map_data("state")
data(us.cities)
us.cities<-subset(us.cities,country.etc!='AK' & country.etc!='HI') # keep only the contiguous US territory

# Plot Cities on US Map using ggvis
ggvis(all_states,props(x=~long,y=~lat))+layer_path(data=by_group(group))+layer_point(data=us.cities)
```
ggvis produces an html page. A svg of the plot is included here.

<embed type="image/svg+xml" src="img/cities.svg" />

(2) Add interactions
* Using tooltip brushing, display the name of the city when hovering over it. 
```{r, eval=FALSE}
show_cities <- function(x) {
  if(is.null(x)) return(NULL)
  temp<-subset(us.cities,lat==x["lat"][[1]] & long==x["long"][[1]])
  if(dim(temp)[1]<1) return(NULL)
  paste(temp$name, collapse="<br />")  
}

ggvis(us.cities, props(x = ~long, y = ~lat)) +layer_point() + layer_path(data=all_states)+ tooltip(show_cities) 

#ggvis(us.cities, props(x= ~long,y = ~ lat)) +  layer(all_states, layer_path(data = by_group(group)))+layer_point() + tooltip(show_cities) 
```
Generates the following picture. 

<embed type="image/svg+xml" src="img/hover_cities.svg" />

A tooltip box shows up and displays the city name when hovering over a dot. But it also displays a blank tooltip box when hovering over a line.  The other problem is the fact that there are lines between states. Could not get the by_group function to work.  Usually nothing was displayed. A really ugly piece of code to fix the lines between states are as follows: 

```{r, eval=FALSE}
states<-unique(all_states$region)
ggvis(us.cities, props(x = ~long, y = ~lat)) +layer_point() + tooltip(show_cities) + 
  layer_path(data=subset(all_states, region==states[1])) +
  layer_path(data=subset(all_states, region==states[2])) +
  layer_path(data=subset(all_states, region==states[3])) +
  layer_path(data=subset(all_states, region==states[4])) +
  layer_path(data=subset(all_states, region==states[5])) +
  layer_path(data=subset(all_states, region==states[6])) +
  layer_path(data=subset(all_states, region==states[7])) +
  layer_path(data=subset(all_states, region==states[8])) +
  layer_path(data=subset(all_states, region==states[9])) +
  layer_path(data=subset(all_states, region==states[10])) +
  layer_path(data=subset(all_states, region==states[11])) +
  layer_path(data=subset(all_states, region==states[12])) +
  layer_path(data=subset(all_states, region==states[13])) +
  layer_path(data=subset(all_states, region==states[14])) +
  layer_path(data=subset(all_states, region==states[15])) +
  layer_path(data=subset(all_states, region==states[16])) +
  layer_path(data=subset(all_states, region==states[17])) +
  layer_path(data=subset(all_states, region==states[18])) +
  layer_path(data=subset(all_states, region==states[19])) +
  layer_path(data=subset(all_states, region==states[20])) +
  layer_path(data=subset(all_states, region==states[21])) +
  layer_path(data=subset(all_states, region==states[22])) +
  layer_path(data=subset(all_states, region==states[23])) +
  layer_path(data=subset(all_states, region==states[24])) +
  layer_path(data=subset(all_states, region==states[25])) +
  layer_path(data=subset(all_states, region==states[26])) +
  layer_path(data=subset(all_states, region==states[27])) +
  layer_path(data=subset(all_states, region==states[28])) +
  layer_path(data=subset(all_states, region==states[29])) +
  layer_path(data=subset(all_states, region==states[30])) +
  layer_path(data=subset(all_states, region==states[31])) +
  layer_path(data=subset(all_states, region==states[32])) +
  layer_path(data=subset(all_states, region==states[33])) +
  layer_path(data=subset(all_states, region==states[34])) +
  layer_path(data=subset(all_states, region==states[35])) +
  layer_path(data=subset(all_states, region==states[36])) +
  layer_path(data=subset(all_states, region==states[37])) +
  layer_path(data=subset(all_states, region==states[38])) +
  layer_path(data=subset(all_states, region==states[39])) +
  layer_path(data=subset(all_states, region==states[10])) +
  layer_path(data=subset(all_states, region==states[41])) +
  layer_path(data=subset(all_states, region==states[42])) +
  layer_path(data=subset(all_states, region==states[43])) +
  layer_path(data=subset(all_states, region==states[44])) +
  layer_path(data=subset(all_states, region==states[45])) +
  layer_path(data=subset(all_states, region==states[46])) +
  layer_path(data=subset(all_states, region==states[47])) +
  layer_path(data=subset(all_states, region==states[48])) +
  layer_path(data=subset(all_states, region==states[49]))
```
* Using tooltip clicking, add a city to the current route.  Make cities that are part of the route bigger in size (and/or change color?) and connect them by a path reflecting the order in which they have been added.

```{r,eval=FALSE}
# Add a column to check if us.cities is on path
us.cities$on_path=(us.cities$name=="heaven") 

# Create an empty path
path<-data.frame(name=character(),
                 country.etc=character(),
                 pop=integer(),
                 lat=numeric(),
                 long=numeric(),
                 capital=integer()
                 )

add_to_path <- function(x) {
  if(is.null(x)) return(NULL)
  temp<-subset(us.cities,lat==x["lat"][[1]] & long==x["long"][[1]])
  if(dim(temp)[1]<1) return(NULL)
  path<<-rbind(path,temp)
  us.cities[us.cities$name==temp$name,]$on_path<<-TRUE
  paste(c("Path:", path$name), collapse="<br />")
}

states<-unique(all_states$region)
ggvis(us.cities, props(x = ~long, y = ~lat)) +layer_point(props(fill=~as.factor(on_path))) + tooltip(show_cities) + 
  layer_path(data=subset(all_states, region==states[1])) +
  layer_path(data=subset(all_states, region==states[2])) +
  layer_path(data=subset(all_states, region==states[3])) +
  layer_path(data=subset(all_states, region==states[4])) +
  layer_path(data=subset(all_states, region==states[5])) +
  layer_path(data=subset(all_states, region==states[6])) +
  layer_path(data=subset(all_states, region==states[7])) +
  layer_path(data=subset(all_states, region==states[8])) +
  layer_path(data=subset(all_states, region==states[9])) +
  layer_path(data=subset(all_states, region==states[10])) +
  layer_path(data=subset(all_states, region==states[11])) +
  layer_path(data=subset(all_states, region==states[12])) +
  layer_path(data=subset(all_states, region==states[13])) +
  layer_path(data=subset(all_states, region==states[14])) +
  layer_path(data=subset(all_states, region==states[15])) +
  layer_path(data=subset(all_states, region==states[16])) +
  layer_path(data=subset(all_states, region==states[17])) +
  layer_path(data=subset(all_states, region==states[18])) +
  layer_path(data=subset(all_states, region==states[19])) +
  layer_path(data=subset(all_states, region==states[20])) +
  layer_path(data=subset(all_states, region==states[21])) +
  layer_path(data=subset(all_states, region==states[22])) +
  layer_path(data=subset(all_states, region==states[23])) +
  layer_path(data=subset(all_states, region==states[24])) +
  layer_path(data=subset(all_states, region==states[25])) +
  layer_path(data=subset(all_states, region==states[26])) +
  layer_path(data=subset(all_states, region==states[27])) +
  layer_path(data=subset(all_states, region==states[28])) +
  layer_path(data=subset(all_states, region==states[29])) +
  layer_path(data=subset(all_states, region==states[30])) +
  layer_path(data=subset(all_states, region==states[31])) +
  layer_path(data=subset(all_states, region==states[32])) +
  layer_path(data=subset(all_states, region==states[33])) +
  layer_path(data=subset(all_states, region==states[34])) +
  layer_path(data=subset(all_states, region==states[35])) +
  layer_path(data=subset(all_states, region==states[36])) +
  layer_path(data=subset(all_states, region==states[37])) +
  layer_path(data=subset(all_states, region==states[38])) +
  layer_path(data=subset(all_states, region==states[39])) +
  layer_path(data=subset(all_states, region==states[10])) +
  layer_path(data=subset(all_states, region==states[41])) +
  layer_path(data=subset(all_states, region==states[42])) +
  layer_path(data=subset(all_states, region==states[43])) +
  layer_path(data=subset(all_states, region==states[44])) +
  layer_path(data=subset(all_states, region==states[45])) +
  layer_path(data=subset(all_states, region==states[46])) +
  layer_path(data=subset(all_states, region==states[47])) +
  layer_path(data=subset(all_states, region==states[48])) +
  layer_path(data=subset(all_states, region==states[49])) +
  click_tooltip(add_to_path)

+ layer_path(data=path)
```

Conversion of ggplot to ggvis
ggvis.rstudio.com/layers.html#layer_path

Workspace: Anything after this is our old code. Feel free to edit. 
===============

```{r, eval=FALSE}
# install ggvis
install.packages("devtools")
library(devtools)
devtools::install_github(c("hadley/testthat", "rstudio/shiny", "rstudio/ggvis"))

# load ggvis
library(ggvis)
library(maps)
library(ggplot2)

# load Map of States, and US Cities data
all_states<-map_data("state")
data(us.cities)
us.cities<-subset(us.cities,lat<55)
us.cities<-subset(us.cities,lat>24)

all_values <- function(x) {
  if(is.null(x)) return(NULL)
  if(x$lat<min(us.cities$lat) | x$lat>max(us.cities$lat)) return(NULL)
  if(x$long<min(us.cities$long) | x$long>max(us.cities$long)) return(NULL)
  t<-subset(us.cities, lat==x$lat)
  t<-subset(t, long==x$long)
  if(dim(t)[1]<1) return(NULL)
  
  paste(t$name, collapse="<br />")
}

ggvis(all_states,props(x=~long,y=~lat))+layer_path(data=by_group(group))+layer_point(data=us.cities)+brush_tooltip(all_values)

dimnames(mtcars)[1]

qvis(us.cities,~long,~lat)+tooltip(all_values)

data(mtcars)
all_values <- function(x) {
  if(is.null(x)) return(NULL)
  paste0(names(x), ": ", format(x), collapse = "<br />")
}

# Display tooltip when hovering over objects
qvis(mtcars, ~wt, ~mpg) + tooltip(all_values)

# Display tooltip when objects are clicked
qvis(mtcars, ~wt, ~mpg) + click_tooltip(all_values)
input_select()

myMTcars

all_values <- function(x) {
  if(is.null(x)) return(NULL)
  class(x)
}

ggvis(myMTcars, props(x=1disp,y=~mpg,size.brush=:=400,key:=~keys))+layer_point()+tooltip(show_model)

myMtcars <- mtcars
myMtcars$keys <- seq(1, nrow(myMtcars))    							 
show_model <- function(x=NULL) {
  if(is.null(x)) return(NULL)
  key <- x["keys"][[1]]
  rownames(myMtcars)[key]
}									 
ggvis(myMtcars, props(x = ~disp, y = ~mpg,  size.brush := 400, key := ~keys)) +
  layer_point() + tooltip(show_model)


ggvis(all_states,props(x=~long,y=~lat))+layer_path(data=by_group(group))+tooltip(show_cities)

+ layer(all_states,layer_path(data=by_group(grou)))
ggvis(us.cities, props(x = ~long, y = ~lat,  size.brush := 400)) +layer_point() + tooltip(show_cities)
+layer_path(props(x=~long,y=~lat),data=all_states)

+ layer_path(props(x=~long,~lat),data=by_group(all_states$group))
```

Verifying if I can commit changes.
----