GGVIS PROJECT
========================================================
**Team:** Junzhao Hu (junhu), Andreea Erciulescu (andreeae), Jennifer Chang (jenchang), Guillermo Basulto-Elias (basulto)

**Description:**

The idea of today's lab is the same as the one two weeks ago: you are asked to provide a shiny applicaiton that allows the user to select US cities to be included in a route across the country.

This time, the applicaiton is supposed to be based on ggvis and enhanced by interactive functionality.

(1) Construct a map of the US using ggvis. Add points of all available cities on top of the map

```{r, eval=FALSE}
# Installs Required Libraries, including ggvis
install.packages("devtools","maps","ggplot2")
library(devtools)
devtools::install_github(c("hadley/testthat", "rstudio/shiny", "rstudio/ggvis"))

# Load Libraries
library(ggvis)
library(maps)
library(ggplot2)

# load Map of States, and US Cities data
all_states<-map_data("state")
data(us.cities)
us.cities<-subset(us.cities,lat>24 & lat<55) # get rid of Alaska and Hawii Cities

# Plot Cities on US Map using ggvis
ggvis(all_states,props(x=~long,y=~lat))+layer_path(data=by_group(group))+layer_point(data=us.cities)
```
ggvis produces an html page. A svg of the plot is included here.

<embed type="image/svg+xml" src="img/cities.svg" />

(2) Add interactions
* Using tooltip brushing, display the name of the city when hovering over it. 
* Using tooltip clicking, add a city to the current route.  Make cities that are part of the route bigger in size (and/or change color?) and connect them by a path reflecting the order in which they have been added.

```{r,eval=FALSE}
# put whatever works here
```

Conversion of ggplot to ggvis
ggvis.rstudio.com/layers.html#layer_path

Workspace: Anything after this is our old code. Feel free to edit. 
===============

```{r, eval=FALSE}
# install ggvis
install.packages("devtools")
library(devtools)
devtools::install_github(c("hadley/testthat", "rstudio/shiny", "rstudio/ggvis"))

# load ggvis
library(ggvis)
library(maps)
library(ggplot2)

# load Map of States, and US Cities data
all_states<-map_data("state")
data(us.cities)
us.cities<-subset(us.cities,lat<55)
us.cities<-subset(us.cities,lat>24)

all_values <- function(x) {
  if(is.null(x)) return(NULL)
  if(x$lat<min(us.cities$lat) | x$lat>max(us.cities$lat)) return(NULL)
  if(x$long<min(us.cities$long) | x$long>max(us.cities$long)) return(NULL)
  t<-subset(us.cities, lat==x$lat)
  t<-subset(t, long==x$long)
  if(dim(t)[1]<1) return(NULL)
  
  paste(t$name, collapse="<br />")
  #paste0(names(x), ": ", format(x), collapse = "<br />")
}

ggvis(all_states,props(x=~long,y=~lat))+layer_path(data=by_group(group))+layer_point(data=us.cities)+brush_tooltip(all_values)

dimnames(mtcars)[1]

qvis(us.cities,~long,~lat)+tooltip(all_values)

data(mtcars)
all_values <- function(x) {
  if(is.null(x)) return(NULL)
  paste0(names(x), ": ", format(x), collapse = "<br />")
}

# Display tooltip when hovering over objects
qvis(mtcars, ~wt, ~mpg) + tooltip(all_values)

# Display tooltip when objects are clicked
qvis(mtcars, ~wt, ~mpg) + click_tooltip(all_values)
input_select()

myMTcars

all_values <- function(x) {
  if(is.null(x)) return(NULL)
  class(x)
}

ggvis(myMTcars, props(x=1disp,y=~mpg,size.brush=:=400,key:=~keys))+layer_point()+tooltip(show_model)

myMtcars <- mtcars
myMtcars$keys <- seq(1, nrow(myMtcars))    							 
show_model <- function(x=NULL) {
  if(is.null(x)) return(NULL)
  key <- x["keys"][[1]]
  rownames(myMtcars)[key]
}									 
ggvis(myMtcars, props(x = ~disp, y = ~mpg,  size.brush := 400, key := ~keys)) +
  layer_point() + tooltip(show_model)
```

Verifying if I can commit changes.
----